Supplementary Materials

### 2018-12-23 Manuscript/sup_mat/sup_mat.Rmd
Sup mat added details

# filter out bad participants 
avg_acc_all <- ls_acc_RT %>%
  filter(observer != 15,
         observer != 25,
         observer != 47,
         observer != 48) %>%
  group_by(observer, targSide) %>%
  summarise(Acc = mean(accuracy))

#### get number of incorrect trials ####
incorrect_trials <- ls_acc_RT %>%
  filter(observer != 15,
         observer != 25,
         observer != 47,
         observer != 48,
         responseKey != "Key_x") %>%
  group_by(accuracy) %>%
  summarise(n = n())

@@

@@

# RT by optimal choice
plt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  ggplot(aes(RT/1000, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt$labels$x <- "Response Time (secs)"
plt$labels$fill <- "Optimal Choice"
plt

# what about RT by number of optimal choices
# only: - correct trials
#       - RT > 300ms
plt2 <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt2

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt3 <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt3

@@

>>>>

# filter out bad participants 
avg_acc_all <- ls_acc_RT %>%
  filter(!observer %in% c(15, 25, 47, 48)) %>%
  group_by(observer, targSide) %>%
  summarise(Acc = mean(accuracy))

#### get number of incorrect trials ####
incorrect_trials <- ls_acc_RT %>%
  filter(!observer %in% c(15, 25, 47, 48),
         responseKey != "Key_x") %>%
  group_by(accuracy) %>%
  summarise(n = n())

@@

# add in log2 RT 
# there is a trial with RT 0 so make sure RT is greater than that too
dat_ACS <- dat_ACS %>%
  mutate(log2_RT = log2(RT)) %>%
  filter(RT > 0)

@@

# RT by optimal choice
plt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt$labels$x <- "Response Time (msecs)"
plt$labels$fill <- "Optimal Choice"

plt1_5 <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ggplot(aes(log2_RT, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt1_5$labels$x <- "log2 transformed Response Time"
plt1_5$labels$fill <- "Optimal Choice"

# plot together 
grid.arrange(plt,plt1_5)

# what about RT by number of optimal choices
# only: - correct trials
#       - RT > 300ms
plt2 <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt2$labels$X <- "No. of Optimal Choices"
plt2$labels$y <- "Mean RT (msecs)"

# same as above but using the log2_RT as criteria to exclude
plt2_5 <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(log2_RT)) %>%
  filter(log2_RT > log2(300),
         log2_RT < log2_RT + 3 * sdev,
         log2_RT > log2_RT - 3 * sdev) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(log2_RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt2_5$labels$x <- "No. Optimal Choices"
plt2_5$labels$y <- "Mean log2 RT"

grid.arrange(plt2, plt2_5)

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt3 <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt3

# RT and Acc, does this help at all?
plt4 <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT), 
            Accuracy = mean(Acc)) %>%
  ggplot(aes(mean_RT, Accuracy, label = SubNo)) +
  geom_point() + 
  geom_text() + 
  theme_bw()
plt4

@@

```{r plotting foraging, echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
# again, what sort of plots are we interester in?

# mean RT by repetition rate? in each condition?
plt <- dat_for %>%
  na.omit() %>%
  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, search_type, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, search_type) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt$labels$y <- "Response Time (secs)"
plt$labels$x <- "Average Repetition Rate"
plt$labels$colour <- "Search Condition"
plt
